rotation runs 2019

### 2019-09-13 inst/documents/rotations_notes.Rmd
getting there with running multiple scenarios

# 11/09/19

This is the new workflow.

@@

@@

~ add option for different insecticides to the experiment file

@@

~ investigate getting runs to name the output file with the date 
~ and create a similarly named metadata file that records run input params 
~ think about moving run control from a rmd to a .R script

>>>>

# 11/09/19
This is the new workflow.

@@

# 12/09/19
sorting mort_or_freq and other inputs in set_run_inputs() and get_one_in()

something I've done means that now the first insecticide is not changed in any scenarios...

linputs <- get_one_in(linmulti, scen_num=1)
linputs <- get_one_in(linmulti, scen_num=2)
linputs <- get_one_in(linmulti, scen_num=3)

linputs <- get_one_in(linmulti, scen_num=4)
linputs <- get_one_in(linmulti, scen_num=5)
linputs <- get_one_in(linmulti, scen_num=6)

# run one scenario
dfres <- do.call(run_rot, linputs)

# 13/09/19

inex <- read_in_expt("_in_expt_rotations_default_one_scenario.csv", nscenarios=1) 
linmulti <- set_run_inputs(inex=inex)
linputs <- get_one_in(linmulti, scen_num=1)
dfres <- do.call(run_rot, linputs)

moving to have male_expo_prop default as 0

@@

CHECK THE DIFFERENCE between linputs in run_rot() which is working compared to the input csv which mostly doesn't work.

~ something is wrong both when mort_or_freq set to mort and freq

~ when set to freq the first insecticide doesn't stop being used
  when set to mort the first insecticide is just used very briefly

~ add log-normal distribution for frequency
~ how to deal with running seq vs rotations
~ there is other stuff I still need in sensi_an_rotations1.Rmd - e.g. post-processing of outputs
~ could I have multiple experiments as columns in the same input file ?

@@

~ investigate getting runs to name the output file with the date 
~ and create a similarly named metadata file that records run input params
